### 2018-03-01 logs/18-02-06.tex
added files

\documentclass{article}
%easy margins
\usepackage[top=.2in, bottom=.4in, left=.8in, right=.8in]{geometry}
%http links in text
\usepackage{hyperref}
%pictures
\usepackage{graphicx}
%quotes
\usepackage{csquotes}
%landscape single pages
\usepackage{lscape}
%inline enumeration
\usepackage[inline]{enumitem}
\usepackage{setspace}
%****************************************************************
% changing font family
\renewcommand{\familydefault}{\sfdefault} %change font

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Chaning font to a local font
%\setmainfont[
%SmallCapsFont = Fontin-SmallCaps.otf,
%BoldFont = Fontin-Bold.otf,
%ItalicFont = Fontin-Italic.otf
%]
%{Fontin.otf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%page title
%\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\doublespacing
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%micromanage font size, the first argument is
%%size of the font, the second line distance
\fontsize{11pt}{26pt}\selectfont

%No page numbers.
\pagenumbering{gobble}
%no indentaion for new paragraphs.
\setlength{\parindent}{0pt}
Good Afternoon Dr. ....,

I am a masters student at Auburn University. I am supervised by Dr. 
Bhattacharya. I am conducting research on HiC datasets. Specifically, 
I am looking at local differences between normal and leukemic cells.
In my research I am using your datasets from the link below:

\url{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_ genome_data/}

I am emailing you since I have a question that I haven't been 
able to resolve. I have been trying different normalization methods on HiC
contact matrices that I have extracted from datasets in link  above
; however, I haven't be able to reproduces contact files that
are here:

\url{http://sysbio.rnet.missouri.edu/bdm_download/chromosome3d/unzipped/Input/HiC/}

I have tried sequential component normalization (SCN)
and pearson correlation but the results are not as smooth
and clean as the ones in the link above. For the sake of reproductibility,
could you let me know how such normalizations were made on the original
HiC contact maps? I would greatly appreciate your response since it will
be a great help in my research.

{\small
\setstretch{0.5}
Regards,\\
Behnam Rasoolian\\
M.Sc. student in Computer science and Software Engineering\\
Auburn University\\
}

\texttt{test.py} \\
I have been playing with HiC data some more. I have tried setting the 
values on and around the main diagonal to 0 and calculate pearson 
correlation matrix. The results where somehow smooth but not quitely.
The constact map corresponding to contact\_All dataset set shows
a smoothness close to what I am seeking.
I have also tried to perform linear transformation on one HiC data 
to 
\end{document}

>>>>

\documentclass{article}
%easy margins
\usepackage[top=.2in, bottom=.4in, left=.8in, right=.8in]{geometry}
%http links in text
\usepackage{hyperref}
%pictures
\usepackage{graphicx}
%quotes
\usepackage{csquotes}
%landscape single pages
\usepackage{lscape}
%inline enumeration
\usepackage[inline]{enumitem}
%for double spaces
\usepackage{setspace}
%****************************************************************
% changing font family
\renewcommand{\familydefault}{\sfdefault} %change font

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Chaning font to a local font
%\setmainfont[
%SmallCapsFont = Fontin-SmallCaps.otf,
%BoldFont = Fontin-Bold.otf,
%ItalicFont = Fontin-Italic.otf
%]
%{Fontin.otf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%page title
%\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setstretch{2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%micromanage font size, the first argument is
%%size of the font, the second line distance
\fontsize{13pt}{13pt}\selectfont

%No page numbers.
\pagenumbering{gobble}
%no indentaion for new paragraphs.
\setlength{\parindent}{0pt}
I have downloaded some files from 
\url{https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE63525}
there are lots of intrachromosomal data in there, corresponding
to (I think!) 11 cell lines. During the correspondense that I had
with University of Missouri (Mr. Oluwadare), he told me that I have
to used the  GM12878 data set it there, which is much larger than
the original \cite{lieberman2009comprehensive} dataset.
There are two inter- and intra-chromosomal data sets there:

\begin{enumerate}
\fontsize{13pt}{3pt}\selectfont
    \item GSE63525\_GM12878\_primary\_interchromosomal\_contact\_matrices.tar.gz\\
          GSE63525\_GM12878\_primary\_intrachromosomal\_contact\_matrices.tar.gz
      \item GSE63525\_GM12878\_combined\_interchromosomal\_contact\_matrices.tar.gz\\
          GSE63525\_GM12878\_combined\_intrachromosomal\_contact\_matrices.tar.gz
\end{enumerate}
I wonder which ones I should use at the moment.

\section*{Things to consider}
\begin{enumerate}
    \item effect of multiple pearson normalizations
    \item revised SCN algorithm
\end{enumerate}
\end{document}

### 2018-03-01 logs/18-02-22.tex
added files

\documentclass{article}
%easy margins
\usepackage[top=.2in, bottom=.4in, left=.8in, right=.8in]{geometry}
%http links in text
\usepackage{hyperref}
%pictures
\usepackage{graphicx}
%quotes
\usepackage{csquotes}
%landscape single pages
\usepackage{lscape}
%inline enumeration
\usepackage[inline]{enumitem}
\usepackage{setspace}
%****************************************************************
% changing font family
\renewcommand{\familydefault}{\sfdefault} %change font

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Chaning font to a local font
%\setmainfont[
%SmallCapsFont = Fontin-SmallCaps.otf,
%BoldFont = Fontin-Bold.otf,
%ItalicFont = Fontin-Italic.otf
%]
%{Fontin.otf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%page title
%\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\doublespacing
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%micromanage font size, the first argument is
%%size of the font, the second line distance
\fontsize{11pt}{26pt}\selectfont

%No page numbers.
\pagenumbering{gobble}
%no indentaion for new paragraphs.
\setlength{\parindent}{0pt}
Good Afternoon Dr. ....,

I am a masters student at Auburn University. I am supervised by Dr. 
Bhattacharya. I am conducting research on HiC datasets. Specifically, 
I am looking at local differences between normal and leukemic cells.
In my research I am using your datasets from the link below:

\url{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_ genome_data/}

I am emailing you since I have a question that I haven't been 
able to resolve. I have been trying different normalization methods on HiC
contact matrices that I have extracted from datasets in link  above
; however, I haven't be able to reproduces contact files that
are here:

\url{http://sysbio.rnet.missouri.edu/bdm_download/chromosome3d/unzipped/Input/HiC/}

I have tried sequential component normalization (SCN)
and pearson correlation but the results are not as smooth
and clean as the ones in the link above. For the sake of reproductibility,
could you let me know how such normalizations were made on the original
HiC contact maps? I would greatly appreciate your response since it will
be a great help in my research.

{\small
\setstretch{0.5}
Regards,\\
Behnam Rasoolian\\
M.Sc. student in Computer science and Software Engineering\\
Auburn University\\
}

\texttt{test.py} \\
I have been playing with HiC data some more. I have tried setting the 
values on and around the main diagonal to 0 and calculate pearson 
correlation matrix. The results where somehow smooth but not quitely.
The constact map corresponding to contact\_All dataset set shows
a smoothness close to what I am seeking.
I have also tried to perform linear transformation on one HiC data 
to 
\end{document}

>>>>

\documentclass{article}
%easy margins
\usepackage[top=.2in, bottom=.4in, left=.8in, right=.8in]{geometry}
%http links in text
\usepackage{hyperref}
%pictures
\usepackage{graphicx}
%quotes
\usepackage{csquotes}
%landscape single pages
\usepackage{lscape}
%inline enumeration
\usepackage[inline]{enumitem}
%to change spacing
\usepackage{setspace}

\usepackage{float}
%****************************************************************
% changing font family
\renewcommand{\familydefault}{\sfdefault} %change font

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Chaning font to a local font
%\setmainfont[
%SmallCapsFont = Fontin-SmallCaps.otf,
%BoldFont = Fontin-Bold.otf,
%ItalicFont = Fontin-Italic.otf
%]
%{Fontin.otf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%page title
%\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\doublespacing
% ****setstrech should always go before fontsize
%\setstretch{2.0}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%micromanage font size, the first argument is
%%size of the font, the second line distance
\fontsize{13pt}{26pt}\selectfont

%No page numbers.
\pagenumbering{gobble}
%no indentaion for new paragraphs.
\setlength{\parindent}{0pt}
I have extracted graphlets for all 23 chromosomes from
the contact maps, using ice normalization and I
have thresholed it (test.py). I then separated individual
orbitals from each cell category and put them together.
That is, I have put orbital 0 from MIT, ALL, RL and CALL4
together and put them in a file. Then I did the same for orbital
1 and put them in a separate file and so forth. I then ran MINE.jar
for each file and captured pairwise MIC values for each orbital.
By doing so, the result would have a dataset of the follwoing shape:
\begin{table}[H]
    \centering
    \begin{tabular}{|c|c|c|c|}
        \hline
        Cell 1 & Cell 2 & Orbital & MIC value\\ \hline
    \end{tabular}
\end{table}
My plan was to find a signinficance of pair-wice MIC values 
fo example, using a
null hypothesis of $H_0: MIC_{MIT-ALL} = 0$. This would mean
That MIT-ALL are totally independent of each other. However,
What we are trying to prove is that they are not the same,
which is different. Actually I have to test this null hypothesis:\\
$H_0: MIC_{MIT-ALL} = 1$\\
which if cannot be rejected, means that the two sets of MIT and ALL
are similar to each other.

In order to validate my method, I have to be able to compare the two
normal cell data that I have, namely, MIT and the one from Rao et. al.
I have to be able to get a high value between the two.

\end{document}
